### 2015-01-21 paper_20_sdo.tex
rearrangement for steps of SDLC

@@

\begin{description}
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

>>>>

The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

\begin{easylist}[itemize]
    & Identify the Work/Task/Project
    && Get Initial Idea 
    && Obtain Details
    & Estimate
    && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
    &&Obtain Approval 
    && Quit or Go Forward
    & Document Requirements
    && Identify the Requirements
    && Detail the Requirements
    & Design The Software
    && Find System Integrations
    && Identify Functional Specs
    && Detail the Functional Specs
    & Development of all the tasks in Design and Requirements
    && Identify the Coding Tasks
    && Write the Code/Develop the solution
    && Write the Unit Tests
    & Test
    && Create Test Plans and Cases
    && Run Test Plans and Cases
    & Deployment
    && Create Deployment Steps
    && Run Deployment Steps
    & Maintenance
    && Capture Bugs
    && Survey Users
\end{easylist}

@@

\begin{description}

    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
    \item[Release] - A collection of projects being put in production on a specified date
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.

### 2015-01-21 paper_70_case-study.tex
rearrangement for steps of SDLC

These are notes

Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
Release - A collection of projects being put in production on a specified date

The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

1. Identify the Work/Task/Project
  1. Get Initial Idea
  2. Obtain Details
2. Estimate
  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
  2. Obtain Approval 
  3. Quit or Go Forward
3. Write BRD
  1. Identify the Requirements
  2. Detail the Requirements
4. Write FSD
  1. Find System Integrations
  2. Identify Functional Specs
  3. Detail the Functional Specs
5. Development of all the tasks in FSD
  1. Identify the Coding Tasks
  2. Write the Code/Develop the solution
  3. Write the Unit Tests
6. Test
  1. Create Test Plans and Cases
  2. Run Test Plans and Cases
7. Deployment
  1. Create Deployment Steps
  2. Run Deployment Steps
8. Maintenance
  1. Capture Bugs
  2. Survey Users
 end of notes

>>>>

\subsection{WITHOUT HISTORICAL DATA}

An MPI calculation with default values.

\subsection{WITH HISTORICAL DATA}

How to create better formulas with historical data.
